Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-06-09 vertical-thermal-review.Rmd
misc

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; Front Royal, VA 22630, USA

@@

## Acknowledgements
Thanks to Valentine Herrmann, Norbert Kunert, Camille Piponiot, Peter B. Boucher and Andrew B. Davies for providing figure materials. 
This manuscript benefited from feedback from Eleinis Ávila-Lovera and the ForestGEO Ecosystems & Climate lab at SCBI.
Funding was provided by the Smithsonian Institution.

>>>>

1. Conservation Ecology Center; Smithsonian National Zoo & Conservation Biology Institute; Front Royal, VA 22630, USA

@@

## Acknowledgements
Thanks to Valentine Herrmann, Norbert Kunert, Camille Piponiot, Peter B. Boucher and Andrew B. Davies for providing figure materials. 
This manuscript benefited from feedback from Eleinis Ávila-Lovera, the ForestGEO Ecosystems & Climate lab at NZCBI, and two anonymous reviewers.
Funding was provided by the Smithsonian Institution.
